The Fates of Merging Supermassive Black Holes and a Proposal for a New Class of X-Ray Sources

### 2020-04-13 paper.tex
Final edits from Andreas, and last-minute formatting prior to submitting.

% mnras_guide.tex
%
% MNRAS LaTeX user guide
%
% v3.0 released 22 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0   September 2013 - May 2015
%    First version: complete rewrite of the user guide
%    Basic structure taken from mnras_template.tex by the same author

@@

\section{Methods}\label{sec:methods}
%\begin{figure}
%\begin{center}
%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_1.png}
%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_65.png}\\
%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_187.png}
%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_217.png}\\
%\caption{default}
%\label{default1}
%\end{center}
%\end{figure*}

@@

\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.  They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.  They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citet{2012MNRAS.423.1992S}, \citet{2013MNRAS.428.1351G}, \citet{2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.

@@

\begin{figure}
%\begin{center}
\includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  $f_\mathrm{bary}$ is the universal baryon fraction as a function of total halo mass.  Purple dots shown are examples of our rescaled stellar masses.  We rescaled our stellar masses at $z=0$ by using a lognormal distribution.  For a given galaxy's dark matter mass, the mean of the distribution was taken to be the point on the abundance matching line at that dark matter mass.  The standard deviation of that mean was taken arbitrarily to be 0.3.}
\label{fig:stellar1}
%\end{center}
\end{figure}

@@

The central density, $\rho_c$, can be found from inverting Equation 5 in Stone and Ostriker 2015 for the galaxy's total mass:

@@

In order to parameterize $r_c$ and $r_h$, we can utilize the relationship between the distribution of light and stellar velocity dispersion at the effective radius, and the shape of the dark matter profile.  The effective radius $R_{e}$ and velocity dispersion at the effective radius $\sigma(R_e)$, respectively, can be obtained from (\citet{2009ApJ...706L..86N}, \citet{2010ApJ...725.2312O}, \citet{2014ApJ...789..156M}):

\begin{equation} \label{re}
R_{e} = 2.5 \mathrm{kpc}\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98},
\end{equation}
\begin{equation} \label{sig}
\sigma(R_{e}) = 190\mathrm{km}\;\mathrm{s}^{-1}\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47},
\end{equation}

We also give $r_c$ an initial value of 100 pc, which is reasonable for a cored massive system.  We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf. Equations 9 and A1-A4 in \cite{2015ApJ...806L..28S}).  The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.  Whether $\sigma_{near}$ or $\sigma_{far}$ is used from Stone-Ostriker is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.

At each timestep in the code, $r_h$ is updated according to the stellar mass and Equations \ref{re} and \ref{sig}.  The core radius, $r_c$, is recalculated only if an orbiting black hole enters within $r_c$.  The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker based on conservation of energy.

@@

\subsubsection{Gravitational wave recoils and escape}
The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than the Schwarzschild radius. At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.

@@

Black holes can also eject each other via strong three-body interactions. We remove SBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy, or that they have achieved escape velocity.

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Ejected black holes span almost the entire mass range, while lower-mass black holes are orbiting and higher mass black holes tended to merge.  Colored arrows along upper x-axis represent median masses of respective sets.  Histogram bars are stacked.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/q_merger_fraction.png}
\caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
\caption{Time required for BHs to merge with host SMBH after galaxy merger.  Form for fitted line is $-0.379M_{BH}+5.766$ in log-log space.}
\label{fig:time_to_merge}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are stacked.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
\caption{Final Radii of remaining orbital black holes at z=0.  Kicked black holes generally had a low likelihood of finding their way back to the center by z=0.  There is a slight inverse relationship between BH mass and final distance from center (solid line).}
\label{fig:mvr}
\end{center}
\end{figure}

\begin{figure}
\vspace{20pt}%
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
\caption{X-ray thermal luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
\label{fig:galgas1}
\end{center}
\end{figure}

\section{Signatures of Orbiting Black Holes}
The large fraction of orbiting black holes predicted by our simulations motivates a back-of-the-envelope calculation to see if orbiting black holes produce detectable signatures. In the following section, we estimate the X-ray thermal luminosities due to gas accreted by these BHs while orbiting through their host galaxies.

@@

\begin{figure}
\vspace{20pt}%
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"rho_0 vs sigma with errors".png}
\caption{Central gas density versus central velocity dispersion.  Purple X's represent central gas densities of the galaxies in this study.  Fit in log space is $\rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 25} \text{  g cm}^{-3}$.}
\label{fig:rho0_vs_sigma}
\end{center}
\end{figure}

\begin{figure}
\vspace{20pt}%
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Tx vs sigma with errors".png}
\caption{X-ray temperature versus central velocity dispersion.  Purple X's represent temperatures of the galaxies in this study.  Fit in log space is $T_x = 10^{2.50*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 6.06} \text{  keV}$.}
\label{fig:Tx_vs_sigma}
\end{center}
\end{figure}

@@

\subsubsection{Black Hole Mass Accretion and Luminosity}
At large distances, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}):
\begin{equation}\label{net_accretion}
    \dot{M}_{B} = \frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  g}\text{ s}^{-1},
\end{equation}
where $\rho$ is the density of the surrounding gas, $C_s$ is the gas sound speed, and $v$ is the velocity of the black hole.

However, due to convective (i.e., inefficient) accretion interior to the Bondi radius (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}), the net accretion to the black hole is often substantially lower than the Bondi-Hoyle accretion.  It can be inferred from the fitting relation given in Equation 31 of \cite{2019MNRAS.486.5377I}:
\begin{subequations}
    \begin{equation}\label{inayoshi_accretion}
        \frac{\dot{M}_{\bullet}}{\dot{M}_{Edd}} \simeq 1.5\times10^{-6}T_7^{-4/5}\times\left(\frac{\alpha}{0.01}\right)^{0.37}\left(\frac{\dot{m}_B}{10^{-3}}\right)^{3/5}\left(\frac{f_c}{0.1}\right)^{2/5},
    \end{equation}
    \begin{equation}\label{mdotb}
        \dot{m}_{B} \equiv \dot{M}_{B}/\dot{M}_{Edd},
    \end{equation}
    \begin{equation}\label{edd_acc}
        \dot{M}_{Edd} \equiv \frac{L_{Edd}}{0.1c^2} \text{  g} \text{ s}^{-1},
    \end{equation}
    \begin{equation}\label{edd_lum}
        L_{Edd} \equiv 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}.
    \end{equation}
\end{subequations}
$\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citet{1973A&A....24..337S}, \citet{1991ApJ...376..214B}, \citet{1995ApJ...445..767M}, \citet{1996ApJ...463..656S}, \citet{1998RvMP...70....1B}, \citet{2004PThPS.155..409S}, \cite{2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citet{2001ApJ...562L.129N}, \citet{2004PhRvL..92d5001M}, and \cite{2019MNRAS.486.5377I}).  The Eddington accretion rate is $\dot{M}_{Edd}$, $c$ is the speed of light, and $L_{Edd}$ is the Eddington luminosity.

Given the above, we estimate the bolometric luminosity of the black holes as:
\begin{subequations}
    \begin{equation}\label{bol_lum}
        L_{Bol} = \epsilon\dot{M}_{\bullet}c^2,
    \end{equation}
    \begin{equation}\label{rad_eff}
        \begin{split}
        \text{log}\;\epsilon = \begin{cases}
                        -1.0-(0.0162/\dot{m})^{4}\;\;\text{for 0.023}\;\leq\;\dot{m}, \\
                        \sum_{n}{}a_{n}(log\;\dot{m})^{n}\;\;\;\;\;\;\;\;\;\text{for}\;10^{-4} <\;\dot{m}\;<\;0.023, \\
                        \sum_{n}{}b_{n}(log\;\dot{m})^{n}\;\;\;\;\;\;\;\;\;\text{for}\;10^{-8} <\;\dot{m}\;\leq\;10^{-4},
                               \end{cases}
        \end{split}
    \end{equation}
\end{subequations}
where $\dot{m}=\dot{M_{\bullet}}/\dot{M}_{Edd}$, and $\epsilon$ is the radiative efficiency (cf. Equation 13 in \citet{2019MNRAS.486.5377I}).  The fitted values are $a_0=-0.807$, $a_1=0.27$, $a_n=0$ ($n\geq2$), $b_0=-1.749$, $b_1=-0.267$, $b_2=-0.07492$, and $b_n=0$ ($n\geq3$).

@@

Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the 17 wandering black holes that were within the influence radius.  In all cases, the final luminosity is higher than the original luminosity.
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
\caption{Difference in X-ray thermal luminosity of wandering black holes within the influence radius of the central black hole.  For each vertical line, red (lower) dots are the originally calculated luminosity, not taking the CBH influence into account.  Green (upper) dots are the final luminosities, taking the central BH influence into account.}
\label{fig:wui}
\end{center}
\end{figure}

\subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.  Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"luminosities_final_final".png}
\caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}
\label{fig:loobhs}
\end{center}
\end{figure}

Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}$ and standard deviation $\sigma=4.5\times10^{3}$.
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
\caption{X-ray Thermal Luminosity Distribution of Orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes. The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
\label{fig:ldobhs}
\end{center}
\end{figure}

@@

\section{Acknowledgements}
The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data. We also thank Renyue Cen, Pieter van Dokkum, Charles Hailey, Zoltan Haiman, Kohei Inayoshi, Sean McWilliams, Taeho Ryu and Nick Stone for useful discussions and insights.  AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

>>>>

% mnras_guide.tex
%
% MNRAS LaTeX user guide
%
% v3.0 released 22 May 2015
% (version numbers match those of mnras.cls)
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

%
% Change log
%
% v3.0   September 2013 - May 2015
%    First version: complete rewrite of the user guide
%    Basic structure taken from mnras_template.tex by the same author

@@

\section{Methods}\label{sec:methods}

@@

\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.  They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.  They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citealt{2012MNRAS.423.1992S, 2013MNRAS.428.1351G, 2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.

@@

\begin{figure}
%\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  $f_\mathrm{bary}$ is the universal baryon fraction as a function of total halo mass.  Purple dots shown are examples of our rescaled stellar masses.  We rescaled our stellar masses at $z=0$ by using a lognormal distribution.  For a given galaxy's dark matter mass, the mean of the distribution was taken to be the point on the abundance matching line at that dark matter mass.  The standard deviation of that mean was taken arbitrarily to be 0.3.}
\label{fig:stellar1}
%\end{center}
\end{figure}

@@

The central density, $\rho_c$, can be found from inverting Equation 5 in  \citet{2015ApJ...806L..28S} for the galaxy's total mass:

@@

In order to parameterize $r_c$ and $r_h$, we can utilize the relationship between the distribution of light and stellar velocity dispersion at the effective radius, and the shape of the dark matter profile.  The effective radius $R_{e}$ and velocity dispersion at the effective radius $\sigma(R_e)$, respectively, can be obtained from (\citealt{2009ApJ...706L..86N, 2010ApJ...725.2312O, 2014ApJ...789..156M}):

\begin{equation} \label{re}
R_{e} = 2.5 \mathrm{kpc}\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98},
\end{equation}
\begin{equation} \label{sig}
\sigma(R_{e}) = 190\mathrm{km}\;\mathrm{s}^{-1}\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47}.
\end{equation}

We also give $r_c$ an initial value of 100 pc, which is reasonable for a cored massive system.  We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf. Equations 9 and A1-A4 in \citealt{2015ApJ...806L..28S}).  The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.  Whether $\sigma_{near}$ or $\sigma_{far}$ is used from \cite{2015ApJ...806L..28S} is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.

At each timestep in the code, $r_h$ is updated according to the stellar mass and Equations \ref{re} and \ref{sig}.  The core radius, $r_c$, is recalculated only if an orbiting black hole enters within $r_c$.  The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in \citet{2015ApJ...806L..28S} based on conservation of energy.

@@

\subsubsection{Gravitational wave recoils and escape}
The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than four times the Schwarzschild radius of the more massive black hole. At the moment of the merger, we also assume that the spin vectors of the two SMBHs are randomly aligned.

@@

Black holes can also eject each other via strong three-body interactions. We remove SMBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy, or that they have achieved escape velocity.

\subsection{Simulation setup}\label{subsec:simset}
For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
\begin{equation}\label{tfric}
    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
\end{equation}
The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.  Their initial velocity was arbitrarily chosen to be the circular velocity at that radius, $v_c = \sqrt{GM(R_e)/R_e}$, with orientation, $v_x$, $v_y$, and $v_z$, randomly chosen.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Ejected black holes span almost the entire mass range, while lower-mass black holes are orbiting and higher mass black holes tended to merge.  Colored arrows along upper x-axis represent median masses of respective sets.  Histogram bars are stacked.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/q_merger_fraction.png}
\caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/time_to_merge.png}
\caption{Time required for BHs to merge with host SMBH after galaxy merger.  Form for fitted line is $-0.379M_{BH}+5.766$ in log-log space.}
\label{fig:time_to_merge}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are stacked.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
\caption{Final radii of remaining orbital black holes at z=0.  Kicked black holes generally had a low likelihood of finding their way back to the center by z=0.  There is a slight inverse relationship between BH mass and final distance from center (solid line).}
\label{fig:mvr}
\end{center}
\end{figure}

\begin{figure}
\vspace{20pt}%
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
\caption{X-ray thermal luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
\label{fig:galgas1}
\end{center}
\end{figure}

\section{Signatures of Orbiting Black Holes}
The large fraction of orbiting black holes found in our simulations motivates a back-of-the-envelope calculation to see if orbiting black holes produce detectable signatures. In the following section, we estimate the X-ray thermal luminosities due to gas accreted by these BHs while orbiting through their host galaxies.

@@

\begin{figure}
\vspace{20pt}%
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"rho_0 vs sigma with errors".png}
\caption{Central gas density versus central velocity dispersion.  Purple X's represent central gas densities of the galaxies in this study.  Fit in log space is $\rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 25} \text{  g cm}^{-3}$.}
\label{fig:rho0_vs_sigma}
\end{center}
\end{figure}

\begin{figure}
\vspace{20pt}%
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Tx vs sigma with errors".png}
\caption{X-ray temperature versus central velocity dispersion.  Purple X's represent temperatures of the galaxies in this study.  Fit in log space is $T_x = 10^{2.50*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 6.06} \text{  keV}$.}
\label{fig:Tx_vs_sigma}
\end{center}
\end{figure}

@@

\subsubsection{Black Hole Mass Accretion and Luminosity}
At large distances, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citealt{1944MNRAS.104..273B} and \citealt{1952MNRAS.112..195B}):
\begin{equation}\label{net_accretion}
    \dot{M}_{B} = \frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  g}\text{ s}^{-1},
\end{equation}
where $\rho$ is the density of the surrounding gas, $C_s$ is the gas sound speed, and $v$ is the velocity of the black hole.

However, due to convective (i.e., inefficient) accretion interior to the Bondi radius (see \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I}), the net accretion to the black hole is often substantially lower than the Bondi-Hoyle accretion.  It can be inferred from the fitting relation given in equation 31 of \cite{2019MNRAS.486.5377I}:
\begin{subequations}
    \begin{equation}\label{inayoshi_accretion}
        \frac{\dot{M}_{\bullet}}{\dot{M}_{Edd}} \simeq 1.5\times10^{-6}T_7^{-4/5}\times\left(\frac{\alpha}{0.01}\right)^{0.37}\left(\frac{\dot{m}_B}{10^{-3}}\right)^{3/5}\left(\frac{f_c}{0.1}\right)^{2/5},
    \end{equation}
    \begin{equation}\label{mdotb}
        \dot{m}_{B} \equiv \dot{M}_{B}/\dot{M}_{Edd},
    \end{equation}
    \begin{equation}\label{edd_acc}
        \dot{M}_{Edd} \equiv \frac{L_{Edd}}{0.1c^2} \text{  g} \text{ s}^{-1},
    \end{equation}
    \begin{equation}\label{edd_lum}
        L_{Edd} \equiv 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}.
    \end{equation}
\end{subequations}
$\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citealt{1973A&A....24..337S, 1991ApJ...376..214B, 1995ApJ...445..767M, 1996ApJ...463..656S, 1998RvMP...70....1B, 2004PThPS.155..409S, 2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citealt{2001ApJ...562L.129N, 2004PhRvL..92d5001M}, and \citealt{2019MNRAS.486.5377I}).  The Eddington accretion rate is $\dot{M}_{Edd}$, $c$ is the speed of light, and $L_{Edd}$ is the Eddington luminosity.

Given the above, we estimate the bolometric luminosity of the black holes as:
\begin{subequations}
    \begin{equation}\label{bol_lum}
        L_{Bol} = \epsilon\dot{M}_{\bullet}c^2,
    \end{equation}
    \begin{equation}\label{rad_eff}
        \begin{split}
        \text{log}\;\epsilon = \begin{cases}
                        -1.0-(0.0162/\dot{m})^{4}\;\;\text{for 0.023}\;\leq\;\dot{m}, \\
                        \sum_{n}{}a_{n}(log\;\dot{m})^{n}\;\;\;\;\;\;\;\;\;\text{for}\;10^{-4} <\;\dot{m}\;<\;0.023, \\
                        \sum_{n}{}b_{n}(log\;\dot{m})^{n}\;\;\;\;\;\;\;\;\;\text{for}\;10^{-8} <\;\dot{m}\;\leq\;10^{-4},
                               \end{cases}
        \end{split}
    \end{equation}
\end{subequations}
where $\dot{m}=\dot{M_{\bullet}}/\dot{M}_{Edd}$, and $\epsilon$ is the radiative efficiency (cf. Equation 13 in \citealt{2019MNRAS.486.5377I}).  The fitted values are $a_0=-0.807$, $a_1=0.27$, $a_n=0$ ($n\geq2$), $b_0=-1.749$, $b_1=-0.267$, $b_2=-0.07492$, and $b_n=0$ ($n\geq3$).

@@

Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the 17 wandering black holes that were within the influence radius.  In all cases, the final luminosity is higher than the original luminosity.
\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
\caption{Difference in X-ray thermal luminosity of wandering black holes within the influence radius of the central black hole.  For each vertical line, red (lower) dots are the originally calculated luminosity, not taking the CBH influence into account.  Green (upper) dots are the final luminosities, taking the central BH influence into account.}
\label{fig:wui}
\end{center}
\end{figure}

\subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.  Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"luminosities_final_final".png}
\caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}
\label{fig:loobhs}
\end{center}
\end{figure}

Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}\,\text{erg s}^{-1}$ and standard deviation $\sigma=4.5\times10^{3}\,\text{erg s}^{-1}$.
\begin{figure}
\begin{center}
\includegraphics[width=1.0\columnwidth]{plots/"Final Luminosities using Kohei factor".png}
\caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes. The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
\label{fig:ldobhs}
\end{center}
\end{figure}

@@

\section{Acknowledgements}
The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data, and Seppo Mikkola for making his \textsc{AR-Chain} code available. We also thank Renyue Cen, Pieter van Dokkum, Charles Hailey, Zoltan Haiman, Kohei Inayoshi, Sean McWilliams, Taeho Ryu and Nick Stone for useful discussions and insights.  AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
